The \dealii{} Library, Version 9.3

### 2021-06-18 9.3/paper.tex
Update 9.3/paper.tex
Co-authored-by: Timo Heister <timo.heister@gmail.com>

The source based installation of \dealii{} or complex toolchains of multiple libraries
working together with \dealii{} can be done with the \candi{} script tool for various
Linux operating systems, within the Windows Subsystem Linux (WSL) and on OSX (experimental).
%
The general assumption is that a C, C++ and Fortran compiler and suitable MPI-compilers
for the base compilers as well as the corresponding development system packages are
available.

>>>>

The source based installation of \dealii{} or complex toolchains of multiple libraries
can be done with the \candi{} script tool for various
Linux operating systems, within the Windows Subsystem Linux (WSL) and on OSX (experimental).
%
The general assumption is that a C, C++ and Fortran compiler and suitable MPI-compilers
for the base compilers as well as the corresponding development system packages are
available.
